Automatic Extraction of JavaScript Formal Semantics from ECMAScript Specifications

### 2019-08-01 icse/compile.tex

By above techniques, we can get the programming language's AST, Parser, and executable steps to run the abstract algorithm in the specification.
But, to run the program with these primitives, Many languages need initial environment to run the program. It is mostly about initialization of builtin types, and it also includes specifying entry point of the program (fetch main function and fill arguments in Java, C, ..)
These environments are sometimes described as steps of algorithm, but mostly it is not. 
In our diagram, we categorized these part as language-dependent environment. It is hard to generate environment automatically, but it is relativly not too heavy to model it compared to modeling numerous algorithms used in runtime.
In this section, we describre how to generate initial environment for ECMAScript to run defined semantics.

Convert to
\begin{itemize}
\item algorithm name => Global Id
\item Builtin Object function name => Heap Object .Code
\item Type function name => Internal Map field
\item Syntax function name => Internal AST semantics field
\end{itemize}

For ECMAScript Specification, initial environment consists of the builtin objects, Intrinsincs, and binding environment of specification steps.

Builtin objects

 In ECMAScript, there is a initial object which have references of builtin object. Each Builtin Object provides fields and function, just as ordinary object. But when its function is called,
 the corresponding step specified in document should be called. To support global object, we make shape of builtin object and its attributes, and then we autoamtically match the step in specification to corresponding field in object by considering its function name.

 Intrinsics

 While Builtin objects can be used to refer itself in ECMAScript language, It is also frequently used in ECMAScript specification. But name of builtin objects
 are defiend for reference in Host language, it needs another name to refer it in specification langauge. Intrinsics are alias for built-in objects. 
 Correspondence between Intrinsic name and Builtin objects are shown in table, so we parse this table to generate global ID to object.

 Binding environment

 In specification, All algorithm has name to refer it, but some algorithms have same names and they are called in context-dependent way.
 \begin{itemize}
  \item Global Algorithm
  \item Type-dependent algorithm
  \item Syntax-dependent algorithm
  \item Builtin object algorithm
  \end{itemize}

 There is four types of algorithm. 
 First is global algorithm that can be called by just name, 
 second is set of algorithms which are bounded in specific type of object, 
 third is set of algorithms which are bounded in AST,
 and forth is set of algorithms which correspond to builtin object function.

 We set builtin object function algorithms when initialzing builtin object, so we descibe about rest three algorithms.

@@

@@

@@

For syntax-dependent algorithm, we insert converted functions in AST structure, and add special expression to call AST-dependent algorithm which requires AST Value and algorithm name.
To insert functions, we gather which AST can be applied to a function. Also, to use subAST structure, we passes subAST in function as argument.

>>>>

In this section, we describre how to generate initial environment for ECMAScript to run defined semantics. 
We can extract programming language's AST, Parser, and executable algorithm in the specification with minimal human effort.
With these primitives, we can build entire system for evaluating target language.

Initial environment of language is mostly about initialization of builtin types, or entry point of the program, etc.
In our diagram, we categorized these part as language-dependent environment.
For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsincs, and Algorithm scope. We will describe how to generate each component.

\subsection{Builtin objects}

 In ECMAScript, there is the object which have references of builtin object. Each Builtin Object provides fields and function, just as ordinary object. When its function is called,
 the corresponding algorithm specified in the document should be called. To support builtin object, we make structure of builtin object and its attributes, and then we autoamtically map corresponding field to the algorithm in specification by matching its function name.

 \subsection{Intrinsics}

 While builtin objects has canonical name to refer itself in ECMAScript language, It is also frequently refered in specification. But name of builtin objects
 are defiend for reference in Host language, so it needs another name to refer it in specification langauge. Intrinsics are alias for built-in objects. 
 Map between Intrinsic name and Builtin objects are available in speicificaion as table form , so we parse this table to generate global identifier to object.

 \subsection{Algorithm scope}

 In specification, All algorithm has name to refer it, but some algorithms have same names and they are called in context-dependent way.
 There is four types of algorithm. 
 \begin{itemize}
  \item Global algorithm: they can be called by name in any context
  \item Type-dependent algorithm: they are bounded in specific type of object
  \item Syntax-dependent algorithm: they are bounded in AST
  \item Builtin function algorithm: they correspond to builtin function
  \end{itemize}

@@

We mapped builtin function algorithms in environment when initialzing builtin object, so we descibe about rest three algorithms.

\subsubsection{Global algorithm}

@@

\subsubsection{Type-dependent algorithm}

@@

 \subsubsection{Syntax-dependent algorithm}
For syntax-dependent algorithm, we insert converted functions in AST structure, and add special expression to call AST-dependent algorithm which requires AST Value and algorithm name.
To insert functions, we gather which AST can be applied to a function. Also, to use subAST structure, we passes subAST in function as argument.
